FireSim2019_ManuscriptFigures

### 2023-03-16 README.rmd
Update README file

corncob-experiment2-pHclasses.R: tests for differentially abundant OTUs in unburned/burned soils after a 24 hr vs. 5 week incubation using corncob

@@

@@

@@

@@

>>>>

corncob-experiment2-TempCutoff.R: tests for differentially abundant OTUs in unburned/burned soils after a 24 hr vs. 5 week incubation using corncob

@@

creating_burn_temp_profiles.R: plot the temperature profiles during simulated burns.

@@

incubations_microbial_respiration.R: calculate C remaining during laboratory incubations as a fraction of initial total C

@@

Merged_paper_figures_Revision_Github.R: Combine lab and field OTU datasets to run ordinations and quantify relative abundance of laboratory-identified trait taxa in field data

@@

Qiime-pipeline-for-FireSim2019-LibCombined.ipynb: steps for sequence processing and taxonomic assignments
